\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-04-26 writeup/2016-04wikipedia-network/wikipedia-network-revtex4-combined.tex
MLE power law for indegree + compilation success

\documentclass[pre,twocolumn,twoside,superscriptaddress,floatfix, aps, 10pt]{revtex4-1}

@@

@@

% Fonts and typesetting settings
\usepackage[sc]{mathpazo}
\usepackage[T1]{fontenc}
\linespread{1.05} % Palatino needs more space between lines
\usepackage{microtype}
\usepackage{textcomp}

@@

\newcommand{\www}[1]{\url{#1}}
\newcommand{\req}[1]{(\ref{#1})}
\newcommand{\Req}[1]{Eq.~(\ref{#1})}

% Lettrines
\usepackage{lettrine}

%useful shortcuts
\def\R{\ensuremath{\mathbb{R}}} %\ensuremath adds math mode, if forgotten
\def\Q{\ensuremath{\mathbb{Q}}}
\def\N{\ensuremath{\mathbb{N}}}
\def\Z{\ensuremath{\mathbb{Z}}}
\def\C{\ensuremath{\mathbb{C}}}

%shorcuts with arguments
\newcommand{\abs}[1]{\left\vert#1\right\vert} %nice absolute values
\newcommand{\bt}[1]{\textbf{#1}} %bold
\newcommand{\eq}[1]{\begin{align*}#1\end{align*}} %aligned equations
\newcommand{\norm}[1]{\left\lVert#1\right\rVert} %vector norm
\renewcommand{\eq}[1]{\begin{align*}#1\end{align*}} %aligned equations

%piecewise function

%\begin{displaymath}
%   f(x) = \left\{
%     \begin{array}{lr}
%       1 & : x \in \mathbb{Q}\\
%       0 & : x \notin \mathbb{Q}
%     \end{array}
%   \right.
%\end{displaymath}

%environment
\newcommand{\tab}{\phantom{ssss}}

\usepackage{hyperref}
\usepackage{color}
\newcommand{\todo}[1]{\noindent\textcolor{blue}{{$\Box$ #1}}}

%colors
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} %dark green color
\definecolor{lightblue}{rgb}{0.149,0.545,0.824} %solarized blue
\definecolor{sred}{rgb}{0.863, 0.196, 0.184} %solarized red

\newcommand{\blue}[1]{{\leavevmode\color{lightblue}{#1}}} %solarized blue 
\newcommand{\green}[1]{{\leavevmode\color{javagreen}{#1}}} %command for green
\newcommand{\red}[1]{{\leavevmode\color{sred}{#1}}} %solarized red
\newcommand{\gray}[1]{{\leavevmode\color[gray]{0.5}{#1}}} %gray text
\newcommand{\Prob}[1]{{\rm Pr}\left(#1\right)}

@@

@@

@@

%TODO:
% Formatting
    % incorporate into template
% Abstract 
    % Our findings... braided network (not sure I understand what this means? braided networks don't come up in the paper)
        % is the idea to say "we developed an algorithm that's generalizable to a broader class of networks?"
% Method
    % what to cite for drainage basin in geomorphology
    % clarify basin discussion of method
    % change name from traversal funnels to non-cycle traversal visits?
% Results
    % run MLE; what do i compare against?
\section{Introduction}

@@

\section{Appendix}
\label{Appendix}

\subsection{Constructing The First Link Network}

To map Wikipedia's First Link Network, we use the freely-available XML dump of the English edition of Wikipedia. 
Rather than rely on a sample of articles from which to generalize, we opted to process the entirety of Wikipedia, 
eliminating any statistical error due to sampling.
We analyze the snapshot provided on November 2014, representing the state of Wikipedia at the time.
The November raw dump consists of 11 million articles: 4.7 million unique articles along with redirects
and disambiguations.
Knowing Wikipedia is an ever-evolving project with 10 edits every second and 750 new articles per day on average
\cite{wiki_edits},
our aim is to characterize the structure of the First Link Network.

Wikipedia renders and stores articles in MediaWiki markup, a markup language with syntax and keywords to format and mark elements in a page. Along with special syntax for links, MediaWiki markup includes templates for audio files, images, and side-bar
information.
While a human could manually identify the first link, to map the entire First Link network of 11 million articles, we needed to programmatically untangled the body text from side-bar, header box, and invalid link elements.

While some libraries exist for MediaWiki Markup,
approaches using existing libraries led to several bugs 
including trouble with nested links, nested parenthesis, unclosed tags, escape characters 
as well as compatibility with other libraries used to parse the XML.
Consequently,  we developed an algorithm for parsing the first link in the XML version of each article.
Our parsing algorithm aimed to: 
1) accurately identify the first link among other page elements, and 
2) efficiently do so---that is without needing for several passes through the data.
To process an article in a single pass, we developed a hierarchical system of flags:
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/flags.pdf}  
  \caption{
    \textbf{Parsing Algorithm of Wikipedia's XML dump.}
The highest flag in the hierarchy indicates a Wikimedia template used to mark an element in the side bar, display an image, link to an external file, or another Wikimedia project outside of Wikipeida. Next, to catch any remaining elements outside the main body we have a second flag for <ref>, <div> elements. Finally, we identify parenthesis to ensure we do not capture a link to a pronunciation key.}
  \label{fig:parsing algorithm}
\end{figure}

The algorithm loops in three-character chunks to account for potentially nested elements, 
shifting by one character steps through the article markup.
If any markup triggers for a flag are detected, a flag is raised. 
Once a flag is raised, we stop processing and proceed to the next character
until the flag's closing markup.
A first link is identified only if Flags 1, 2, and 3 are all off.
In this case, the entire link is retrieved. 
We then confirm the link is valid by filtering for MediaWiki keywords indicating external page or other projects
as well as common file extensions for 
images, audio files, and the like 
\cite{media_wiki_templates}.
The first link of an article is then the earliest valid link with unraised flags.

To process the entirety of Wikipedia, we distributed the parsing and processing of the XML dump
across 112 cores of the UVM supercomputer cluster
\cite{vacc}.
We then joined the results to form a hash table containing every Wikipedia article and its corresponding
first link. The resulting network map is the basis of our analysis.
An online appendix containing all of the code and data used can be accessed \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.

\bibliography{wikipedia-network}{}
\bibliographystyle{plain}

>>>>

\documentclass[pre,twocolumn,twoside,byrevtex,superscriptaddress,floatfix]{revtex4-1}

@@

\usepackage{color}
\newcommand{\todo}[1]{\noindent\textcolor{blue}{{$\Box$ #1}}}

@@

@@

\newcommand{\avg}[1]{\left\langle#1\right\rangle}
\newcommand{\tavg}[1]{\langle#1\rangle}

\newcommand{\LavgHa}[2]{\tavg{L_{#1,#2}}}
\newcommand{\LavgHaN}[2]{\tavg{L_{#1,#2}}}
\newcommand{\Lavg}{\tavg{L}}

\newcommand{\sindex}[1]{}
\newcommand{\nindex}[1]{}

\newcommand{\etal}{\textit{et al.}}
\newcommand{\www}[1]{\url{#1}}
\newcommand{\req}[1]{(\ref{#1})}
\newcommand{\Req}[1]{Eq.~(\ref{#1})}

% lettrines
\usepackage{lettrine}

\newcommand{\tbf}{\textbf}
\newcommand{\tit}{\textit}

\newcommand{\dee}[1]{\mbox{d}#1}
\newcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\pdiffsq}[2]{\frac{\partial^2 #1}{{\partial #2}^2}}
\newcommand{\diff}[2]{\frac{{\rm d}#1}{{\rm d}#2}}
\newcommand{\diffsq}[2]{\frac{{\rm d}^{2}#1}{{\rm d} {#2}^2}}
\newcommand{\tdiff}[2]{\mbox{d} #1/\mbox{d} #2}
\newcommand{\tdiffsq}[2]{\mbox{d}^{2} #1/\mbox{d} {#2}^2}
\newcommand{\tpdiff}[2]{\partial #1/\partial #2}
\newcommand{\tpdiffsq}[2]{\partial^2 #1/\partial {#2}^2}
\newcommand{\postdee}[1]{\,\mbox{d}#1}

\newcommand{\Prob}[1]{{\rm Pr}\left(#1\right)}

% \newcommand{\kstar}{d^{\ast}}
% \newcommand{\kstari}{k_i^\ast}
\newcommand{\kstar}{d^\ast}
\newcommand{\kstari}{d_i^\ast}

\newcommand{\dstar}{d^\ast}
\newcommand{\dstari}{d_i^\ast}

\newcommand{\phifix}{{\phi^{\ast}}}
\newcommand{\phifixc}{{\phi_c^{\ast}}}
\newcommand{\phifixb}{{\phi_b^{\ast}}}

\newcommand{\phiiactive}{\phi_{i,t}}

\newcommand{\phiiup}{{\phi_{i,\rm on}}}
\newcommand{\phiidown}{{\phi_{i,\rm off}}}

\newcommand{\phiup}{{\phi_{\rm on}}}
\newcommand{\phidown}{{\phi_{\rm off}}}

\newcommand{\Gfun}{G}

\newcommand{\dstardist}{g}
\newcommand{\dosedist}{f}
\newcommand{\dosedistk}{f^{k\star}}

% chaotic contagion
\newcommand{\edgeinfprob}{\rho}
\newcommand{\nodeinfprob}{\phi}

\newcommand{\avgdegree}{k_{\rm avg}}

\newcommand{\stateA}{S_{0}}
\newcommand{\stateB}{S_{1}}

\newcommand{\lcce}{H}

\newcommand{\effectivecount}{f_{q,\textnormal{exp}}}
\newcommand{\effectivecountq}[1]{f_{#1,\textnormal{exp}}}

\newcommand{\simonrho}{\rho}
\newcommand{\zipfexponent}{\alpha}

\newcommand{\partitionprob}{q}
\newcommand{\partitiontype}[1]{$\partitionprob$$=$$#1$}

\newcommand{\onehalf}{\frac{1}{2}}
\newcommand{\onequarter}{\frac{1}{4}}

\newcommand{\clgamma}{\hat{\zipfexponent}}
\newcommand{\xmin}{r_{\textnormal{max}}}
\newcommand{\kstat}{D}
\newcommand{\clp}{\mbox{$p$-value}}
\newcommand{\sigamma}{1-\simonrho}

@@

\bibliographystyle{unsrtabbrv}

@@

\pacs{89.65.-s,89.75.Da,89.75.Fb,89.75.-k}

@@

\section{Introduction}

@@

\begin{thebibliography}{10}

\bibitem{clauson2008scope}
K.~A. Clauson, H.~H. Polen, M.~N.~K. Boulos, and J.~H. Dzenowagis.
\newblock Scope, completeness, and accuracy of drug information in wikipedia.
\newblock {\em Annals of Pharmacotherapy}, 42(12):1814--1821, 2008.

\bibitem{stats}
Wikipedia.
\newblock Wikipedia:statistics. from wikipedia, the free encyclopedia.
\newblock [Online; accessed 22-April-2016].

\bibitem{wiki_edits}
E.~Zachte.
\newblock Wikipedia statistics: edits per month, April 2016.
\newblock [Online; accessed 22-April-2016].

\bibitem{wiki_views}
Wikipedia.
\newblock Page views for wikipedia, non-mobile site, normalized.
\newblock [Online; accessed 22-April-2016].

\bibitem{iba2010analyzing}
T.~Iba, K.~Nemoto, B.~Peters, and P.~A. Gloor.
\newblock Analyzing the creative editing behavior of wikipedia editors: Through
  dynamic social network analysis.
\newblock {\em Procedia-Social and Behavioral Sciences}, 2(4):6441--6456, 2010.

\bibitem{samoilenko2016linguistic}
A.~Samoilenko, F.~Karimi, D.~Edler, J.~Kunegis, and M.~Strohmaier.
\newblock Linguistic neighbourhoods: explaining cultural borders on wikipedia
  through multilingual co-editing activity.
\newblock {\em EPJ Data Science}, 5(1):1, 2016.

\bibitem{holman2008comparison}
L.~Holman~Rector.
\newblock Comparison of wikipedia and other encyclopedias for accuracy,
  breadth, and depth in historical articles.
\newblock {\em Reference services review}, 36(1):7--22, 2008.

\bibitem{giles2005internet}
J.~Giles.
\newblock Internet encyclopaedias go head to head.
\newblock {\em Nature}, 438(7070):900--901, 2005.

\bibitem{halavais2008analysis}
A.~Halavais and D.~Lackaff.
\newblock An analysis of topical coverage of wikipedia.
\newblock {\em Journal of Computer-Mediated Communication}, 13(2):429--440,
  2008.

\bibitem{hill2013wikipedia}
B.~M. Hill and A.~Shaw.
\newblock The wikipedia gender gap revisited: Characterizing survey response
  bias with propensity score estimation.
\newblock {\em PloS one}, 8(6):e65782, 2013.

\bibitem{williams2015identifying}
J.~R. Williams, E.~M. Clark, J.~P. Bagrow, C.~M. Danforth, and P.~S. Dodds.
\newblock Identifying missing dictionary entries with frequency-conserving
  context models.
\newblock {\em Physical Review E}, 92(4):042808, 2015.

\bibitem{banerjee2007clustering}
S.~Banerjee, K.~Ramanathan, and A.~Gupta.
\newblock Clustering short texts using wikipedia.
\newblock In {\em Proceedings of the 30th annual international ACM SIGIR
  conference on Research and development in information retrieval}, pages
  787--788. ACM, 2007.

\bibitem{gabrilovich2007computing}
E.~Gabrilovich and S.~Markovitch.
\newblock Computing semantic relatedness using wikipedia-based explicit
  semantic analysis.
\newblock In {\em IJCAI}, volume~7, pages 1606--1611, 2007.

\bibitem{cucerzan2007large}
S.~Cucerzan.
\newblock Large-scale named entity disambiguation based on wikipedia data.
\newblock In {\em EMNLP-CoNLL}, volume~7, pages 708--716, 2007.

\bibitem{kamps2009wikipedia}
J.~Kamps and M.~Koolen.
\newblock Is wikipedia link structure different?
\newblock In {\em Proceedings of the second ACM international conference on Web
  search and data mining}, pages 232--241. ACM, 2009.

\bibitem{page1999pagerank}
L.~Page, S.~Brin, R.~Motwani, and T.~Winograd.
\newblock The pagerank citation ranking: bringing order to the web.
\newblock {\em Stanford InfoLab}, 1999.

\bibitem{chakrabarti2001integrating}
S.~Chakrabarti.
\newblock Integrating the document object model with hyperlinks for enhanced
  topic distillation and information extraction.
\newblock In {\em Proceedings of the 10th international conference on World
  Wide Web}, pages 211--220. ACM, 2001.

\bibitem{wiki_train}
Wikipedia.
\newblock Train --- wikipedia{,} the free encyclopedia, 2016.
\newblock [Online; accessed 22-April-2016].

\bibitem{xkcd}
xkcd.
\newblock xkcd: Extended mind.
\newblock [Online; accessed 22-April-2016].

\bibitem{mat_blog}
M.~Kelcey.
\newblock do all first links on wikipedia lead to philosophy?
\newblock [Online; accessed 22-April-2016].

\bibitem{Ilmari_first_links}
Wikipedia.
\newblock User:ilmari karonen/first link.
\newblock [Online; accessed 22-April-2016].

\bibitem{bob_west}
B.~West.
\newblock Wikipedia's fixed point.
\newblock [Online; accessed 22-April-2016].

\bibitem{Bolton2007}
M.~B. Bolton.
\newblock The taxonomy of ideas in locke's essay.
\newblock In L.~Newman, editor, {\em The Cambridge Companion to Locke's}.
  Cambridge University Press, 2007.

\bibitem{descartes}
K.~Smith.
\newblock Descartes' theory of ideas.
\newblock In E.~N. Zalta, editor, {\em The Stanford Encyclopedia of
  Philosophy}. Spring 2014 edition, 2014.

\bibitem{aristotle}
P.~Studtmann.
\newblock Aristotle's categories.
\newblock In E.~N. Zalta, editor, {\em The Stanford Encyclopedia of
  Philosophy}. Summer 2014 edition, 2014.

\bibitem{hist_thesaurus}
O.~E. Dictionary.
\newblock What is the historical thesaurus of the oed - oxford english
  dictionary.
\newblock [Online; accessed 22-April-2016].

\bibitem{newman2003structure}
M.~E. Newman.
\newblock The structure and function of complex networks.
\newblock {\em SIAM review}, 45(2):167--256, 2003.

\bibitem{eubank2004modelling}
S.~Eubank, H.~Guclu, V.~A. Kumar, M.~V. Marathe, A.~Srinivasan, Z.~Toroczkai,
  and N.~Wang.
\newblock Modelling disease outbreaks in realistic urban social networks.
\newblock {\em Nature}, 429(6988):180--184, 2004.

\bibitem{newman2002random}
M.~E. Newman, D.~J. Watts, and S.~H. Strogatz.
\newblock Random graph models of social networks.
\newblock {\em Proceedings of the National Academy of Sciences}, 99(suppl
  1):2566--2572, 2002.

\bibitem{horton1945erosional}
R.~E. Horton.
\newblock Erosional development of streams and their drainage basins;
  hydrophysical approach to quantitative morphology.
\newblock {\em Geological society of America bulletin}, 56:275--370, 1945.

\bibitem{dodds1999unified}
P.~S. Dodds and D.~H. Rothman.
\newblock Unified view of scaling laws for river networks.
\newblock {\em Physical Review E}, 59(5):4865, 1999.

\bibitem{garlaschelli2003universal}
D.~Garlaschelli, G.~Caldarelli, and L.~Pietronero.
\newblock Universal scaling relations in food webs.
\newblock {\em Nature}, 423(6936):165--168, 2003.

\bibitem{scientology}
.~USA Today.~Gannett.
\newblock Leah remini on scientology: What we learned from 20/20.
\newblock [Online; accessed 22-April-2016].

\bibitem{weddings}
SoundVision.com.
\newblock Wedding statistics in the united states.
\newblock [Online; accessed 22-April-2016].

\bibitem{wagner2015s}
C.~Wagner, D.~Garcia, M.~Jadidi, and M.~Strohmaier.
\newblock It's a man's wikipedia? assessing gender inequality in an online
  encyclopedia.
\newblock {\em arXiv preprint arXiv:1501.06307}, 2015.

\bibitem{reddit}
Reddit.
\newblock Almost every wikipedia page links to philosophy if you keep clicking
  the first link in every article.
\newblock [Online; accessed 22-April-2016].

\end{thebibliography}

\clearpage

### 2016-04-26 writeup/wikipedia-network.tex
MLE power law for indegree + compilation success

%TODO:
% Formatting
    % incorporate into template
% Abstract 
    % Our findings... braided network (not sure I understand what this means? braided networks don't come up in the paper)
        % is the idea to say "we developed an algorithm that's generalizable to a broader class of networks?"
% Method
    % what to cite for drainage basin in geomorphology
    % clarify basin discussion of method
    % change name from traversal funnels to non-cycle traversal visits?
% Results
    % run MLE; what do i compare against?
\section{Introduction}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/articles_ndegree.png}
  \caption{
    \textbf{Highest Ranking Articles by in-degree.}
    We rank each article by the number of direct first links to the article (in-degree). The highest-ranking articles tend to represent geographical and biological abstractions. A full online appendix of the results and data is available \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.}
  \label{fig:indegree list}
\end{figure}
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/ndegree_loglog.png}
  \caption{
    \textbf{FLN Degree Distribution.}
We fit the in-degree distribution with a linear $\log_{10}-\log_{10}$ model. 
The result is a 
an excellent fit with a Pearson's Correlation Coefficient of $-0.98$, yielding a 
power law rank exponent $\alpha = -0.788$ and a size exponent $\gamma = -0.266$. 
}
  \label{fig:degree distribution}
\end{figure}

@@

The FLN's in-degree exhibits a decaying power law distribution where a few articles 
receive most direct first references, while most articles receive few or none.
The average in-degree for all 11 million articles is 3.6 direct first links with a standard deviation of 89.5.
Less than $1\%$ of articles have more than 100 direct first links and $75\%$ of articles
have fewer than 9. 
We fit the in-degree distribution against each article's rank with a log-log (base 10) linear regression model
(see Fig.~\ref{fig:degree distribution}).
We obtain a Pearson's Correlation Coefficient of $-0.98$
with a corresponding  power law rank exponent $\alpha = -0.788$ and a size exponent $\gamma = -0.266$.

@@

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
We fit the distribution of traversal visits against article rank with a log-log (base 10) linear regression model log-log model and uncover two regimes: 
with a cutoff rank of $10^{5}$.
The top regime ($\log_{10}$(rank) $< 5$) has a Pearson's Correlation 
Coefficient of $-0.99$ 
with a corresponding power law rank exponent 
$\alpha = -1.23$ and a size exponent $\gamma = 0.187$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion on cycles).
The bottom regime has a Pearson's Correlation Coefficient of $-0.93$
with a corresponding power law rank exponent 
$\alpha = -0.579$ and a size exponent $\gamma = -0.727$.}
  \label{fig:Distribution of Visits}

>>>>

%TODO:
% Formatting
    % incorporate into template
% Abstract 
    % Our findings... braided network (not sure I understand what this means? braided networks don't come up in the paper)
        % is the idea to say "we developed an algorithm that's generalizable to a broader class of networks?"
% Method
    % what to cite for drainage basin in geomorphology
    % clarify basin discussion of method
    % cite power law papers (clauset and package)
% Results
    % run MLE; what do i compare against?
\section{Introduction}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/articles_ndegree.png}
  \caption{
    \textbf{Highest Ranking Articles by in-degree.}
    We rank each article by the number of direct first links to the article (in-degree). The highest-ranking articles tend to represent geographical and biological abstractions. A full online appendix of the results and data is available \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.}
  \label{fig:indegree list}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/ndegree_loglog.png}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the indegree distribution against rank for all articles with an indegree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the indegree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$.
}
  \label{fig:degree distribution}
\end{figure}

@@

The FLN's in-degree exhibits a decaying power law distribution where a few articles 
receive most direct first references, while most articles receive few or none.
The average in-degree for all 11 million articles is 3.6 direct first links with a standard deviation of 89.5.
Less than $1\%$ of articles have more than 100 direct first links and $75\%$ of articles
have fewer than 9. 
We plot the in-degree distribution against each article's rank with a log-log (base 10) and fit the data to a power law 
distribution using the Maximum Likelihood Estimator with xmin as the indegree minimizing Kolmogorov-Smirnov distance.
(see Fig.~\ref{fig:degree distribution}).
We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$. 
Finally, we compare the fit against alternative distributions using a Kolmogorov-Smirnov Test. We find a significant log likelihood ratio favoring a  truncated power law ($R < 0, p=4.5\times10^{-13}$) given the limits on the maximum possible indegree.  We find an inconclusive log likelihood ratio for a lognormal distribution and significant log likelihood ratios favoring a power law fit to an exponential ($R  > 0, p=0$) and to a stretched exponential ($R > 0, p = 3.0\times10^{-50}$).

@@

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
We fit the distribution of traversal visits against article rank with a log-log (base 10) linear regression model log-log model and uncover two regimes: 
with a cutoff rank of $10^{5}$.
The top regime ($\log_{10}$(rank) $< 5$) has a Pearson's Correlation 
Coefficient of $-0.99$ 
with a corresponding power law rank exponent 
$\alpha = -1.23$ and a size exponent $\gamma = 0.187$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion on cycles).
The bottom regime has a Pearson's Correlation Coefficient of $-0.93$
with a corresponding power law rank exponent 
$\alpha = -0.579$ and a size exponent $\gamma = -0.727$.}
  \label{fig:Distribution of Visits}
\end{figure}
